---
title: "Simplifying Manual Coding Exercises - Raw Data Prep"
author: "Brendon Kaufman"
date: "6/15/2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE)

library(tidyverse)
library(googlesheets4)

```

A manual coding exercise is a methodology for analyzing text data where analysts read through units of text data and label it for the presence or absence of a set number of themes (called codes) in order to quantify the frequency of those themes in the data. This series of RMarkdown documents is part of a series (based on [these slides](https://docs.google.com/presentation/d/186nlOl_pF6Xn63jRMM1Xq0RF8YnDiBtAdOBc_laLDMQ/edit#slide=id.g226e05ac205_1_113)) aimed at simplifying this process by taking advantage of R and RStudio. Note that this workflow is best done within an **RStudio Project Folder.**

This RMarkdown document takes a data set of raw text data and prepares it for a manual coding exercise in Google Sheets. It does this through the following steps:

1.  Reads the data from a saved .csv file in an RStudio Project to a dataframe
2.  Adds columns to the dataframe for codes that will be used to label the text data
3.  Writes the dataframe to a Google Sheet that can be used to label the text data

```{r load-in-data}

# Read in text data from .csv to dataframe

text_data_df <- read_csv("sample_text_data.csv")

```

```{r create-columns-for-codes}

# Create empty columns for codes that will be used to label the text data
# Note that each code starts with "code_" so that we will be able to easily
# identify and select the columns that refer to codes later in analysis

text_data_df_columns_added <- text_data_df %>%
  add_column(code_ui = "",
             code_customer_service = "",
             code_buttons = "",
             code_other = ""
             ) 


```

```{r write-csv-to-google-sheet}

# Writes dataframe to a designated Google Sheet

# Designate Google Sheet url and sheet name

coding_sheet_google_file_id <- "https://docs.google.com/spreadsheets/d/1SnfiqYZ8qDDRT2iQHlWTpfxSqp7nbdiHUpqsEFTcWfg/edit#gid=1273390617"
sheet_name = "text_data_coding"

# Write dataframe to that sheet

write_sheet(data = text_data_df_columns_added,
            ss = coding_sheet_google_file_id,
            sheet = sheet_name)

# Autofit cells to the text data to make it look a little nicer

range_autofit(ss = coding_sheet_google_file_id, 
              sheet = sheet_name,
              dimension = c("columns", "rows"))

```
