---
title: "Simplifying Manual Coding Exercises - Coded Data Prep"
author: "Brendon Kaufman"
date: "6/15/2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE)

library(tidyverse)
library(googlesheets4)

```

A manual coding exercise is a methodology for analyzing text data where analysts read through individual pieces of text data and label it for the presence or absence of a set number of themes (called codes) in order to quantify the frequency of those themes in the data. This series of RMarkdown documents is part of a series (based on [these slides](https://docs.google.com/presentation/d/186nlOl_pF6Xn63jRMM1Xq0RF8YnDiBtAdOBc_laLDMQ/edit#slide=id.g226e05ac205_1_113)) aimed at simplifying this process by taking advantage of R and RStudio. Note that this workflow is best done within an **RStudio Project Folder.**

This RMarkdown document takes a Google Sheet of coded raw text data and prepares it for analysis in RStudio. It does this through the following steps:

1.  Reads coded data from a Google Sheet to a dataframe
2.  Saves the dataframe locally to the folder associated with an RStudio Project

```{r read-in-coded-data}

# Reads coded data from a Google Sheet to a dataframe

# Designate Google Sheet url and sheet name

coding_sheet_google_file_id <- "https://docs.google.com/spreadsheets/d/1SnfiqYZ8qDDRT2iQHlWTpfxSqp7nbdiHUpqsEFTcWfg/edit#gid=1273390617"
sheet_name = "text_data_coding"

coded_data_df <- read_sheet(ss = coding_sheet_google_file_id,
                            sheet = sheet_name,
                            range = "A1:E11")

```

```{r save-dataframe-to-csv}

# Save dataframe to .csv file in RStudio Project

write_csv(coded_data_df, "coded_data_df.csv")
```
