---
title: "Simplifying Manual Coding Exercises - Analysis and Visualization"
author: "Brendon Kaufman"
date: "6/15/2023"
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

library(tidyverse)
library(scales)

```

A manual coding exercise is a methodology for analyzing text data where analysts read through individual pieces of text data and label it for the presence or absence of a set number of themes (called codes) in order to quantify the frequency of those themes in the data. This series of RMarkdown documents is part of a series (based on [these slides](https://docs.google.com/presentation/d/186nlOl_pF6Xn63jRMM1Xq0RF8YnDiBtAdOBc_laLDMQ/edit#slide=id.g226e05ac205_1_113)) aimed at simplifying this process by taking advantage of R and RStudio. Note that this workflow is best done within an **RStudio Project Folder.**

This RMarkdown document takes a .csv file coded raw text data, prepares that data for analysis and quantifies how often a given code occurs among the data. It does this through the following steps:

1.  Reads coded data from a .csv to a dataframe
2.  Prepares the dataframe for analysis including getting rid of uncoded data
3.  Creates an analysis dataframe quantifying how often codes exist in the data
3.  Creates a data visualization displaying how often codes exist in the data

```{r load-coded-text-data}

# Reads coded data from a .csv to a dataframe

coded_data_df <- read_csv("coded_data_df.csv") 

```

```{r prepare-dataframe-for-analysis}

# Prepares the dataframe for analysis including getting rid of uncoded data

coded_data_df_prepared <- coded_data_df %>%
  mutate(across(contains("code_"), # Changes all cells marked "x" for presence of code to boolean TRUE to facilitate counting
                .fns = function(.x) case_when(.x == "x" ~ TRUE,
                                              TRUE ~ FALSE))) %>%
  rowwise() %>%
  mutate(is_coded = sum(c_across(starts_with("code_"))) > 0) %>% # Determines if row has been coded or not
  ungroup() %>%
  filter(is_coded) # Gets rid of rows that don't have any columns coded

```


```{r create-analysis-dataframe}

# Creates an analysis dataframe quantifying how often codes exist in the data

coded_data_df_analysis <- coded_data_df_prepared %>%
  summarise(across(contains("code_"), # Quantifies % of rows with each code
                   .fns = function(.x) round(mean(.x), 2))) %>% 
  pivot_longer(cols = contains("code_"), # Reformats columns for visualization
               names_to = "code", 
               values_to = "proportion_of_rows") %>%
  mutate(code_plain_text = case_when(code == "code_ui" ~ "UI", # Adds plain text column for visualization
                                    code == "code_customer_service" ~ "Customer Service",
                                    code == "code_buttons" ~ "Buttons",
                                    code == "code_other" ~ "Other"),
         .after = code)  # Places new column after code column

```

```{r plot-data, fig.width = 14, fig.height= 6}

# Creates a data visualization displaying how often codes exist in the data

ggplot(coded_data_df_analysis) +
  
  geom_col(aes(x = reorder(code_plain_text, proportion_of_rows), y = proportion_of_rows),
           fill = "#237EA3") + # Bar plot ordered by proportion of rows
  
  geom_text(aes(x = code_plain_text, y = proportion_of_rows, label = percent(proportion_of_rows)),
            nudge_y = 0.02,
            size = 4) + # Adds a text label above the bars
  
  labs(x = "", y = "Proportion of pieces of text data",
       title = "Proportion of pieces of text data with theme",
       subtitle = paste0("Pieces of text data can have multiple tags (n = ",
                        nrow(coded_data_df_prepared),
                        ")")) + # Adds labels to axes including a dynamic one for sample size
  
  coord_flip() + # Flips plot because these plots are often best displayed horizontally
  
  theme_bw()



```
